Through the eyes of the teacher

### 2021-02-09 paper_1/paper_1_supplement.tex
update GRI

\hypertarget{data-collection}{%
\subsection{Data collection}\label{data-collection}}

@@

For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig. The subjects were divided into groups of four, so the study was conducted on two different sessions. All participants were asked to hold a 10-minute lesson. The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering the questionnaire.

By using mobile eye-trackers, the gaze and behavior of the experts and novices was recorded during the lesson. In addition, the speech and sounds and voices were recorded with an audio recorder installed in the middle of the Lab. Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles. One camera was installed to film the class from the side. Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back. Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.

The lessons recorded on video were coded in a post-hoc procedure with a coding software by previously trained raters. The statistical data have been analyzed by using the program RStudio {[}Link: \url{https://rstudio.com/}{]}.

\hypertarget{measures}{%
\subsection{Measures}\label{measures}}

\hypertarget{questionnaire-data}{%
\subsubsection{Questionnaire Data}\label{questionnaire-data}}

\emph{Describe how we collect questionnaire data (paper or online). Add some basic information about the structure of the questionnaire.}

The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes.
The scales on the quality of teaching are a validated questionnaire (Helmke et al. (2014)). Whereas the scales on the teacher's presence behaviour were derived from the research literature (Brophy (1986); Kiel, Frey, Weiß, and Weiss (2013); Kounin (2006); Marzano (2007); Nolting (2012)) and were used in the pilot for the first time.

@@

\includegraphics{paper_1_supplement_files/figure-latex/boxplot scales-1.pdf}
\newpage
Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment. The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.

\includegraphics{paper_1_supplement_files/figure-latex/Duration speaking time-1.pdf}
\newpage

\hypertarget{eye-tracking-equipment}{%
\subsubsection{Eye-tracking equipment}\label{eye-tracking-equipment}}

A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements. The head unit is a measuring device with different sensitive sensors. A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds. Infrared light illuminators support the eye tracking sensors which record the eye orientation. The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second. The scene camera has a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height). The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.

The Tobii Pro Glasses 2 software allows for non-screen based recordings of a participants' attention while moving in real-world settings. The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video. In order to map multiple recordings to AOIs, it is necessary to import the eye-tracking recordings into the Tobii Pro Analyzer software. Also, it is necessary to create a reference image of the scene in which one wishes to plot the gaze data (i.e.~snapshot). Once the snapshot is imported, the gaze recordings of multiple recordings can be mapped to the reference image and analyzed in aggregated form. Tobii Pro does not allow to do AOI based analyses within Pro Lab. Also, the dependency on snapshot reference images makes this approach impractical when working in different settings, i.e.~different classrooms with various participants. Finally, mapping gaze to people or any moving objects complicated the analyses further.

\hypertarget{eye-tracking-data}{%
\subsubsection{Eye-Tracking Data}\label{eye-tracking-data}}

>>>>

\hypertarget{procedure-data-collection}{%
\subsection{Procedure/ Data collection}\label{procedure-data-collection}}

\hypertarget{set-up}{%
\subsubsection{Set up}\label{set-up}}

For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig. The subjects were divided into groups of four, so the study was conducted on two different sessions. All participants were asked to hold a 10-minute lesson. The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering questionnaires.

@@

\hypertarget{questionnaire-data}{%
\subsubsection{Questionnaire data}\label{questionnaire-data}}

After each mini-lesson, the subjects answered items on the teaching quality using a validated questionnaire ((Helmke et al. (2014))) and scales on the teacher's presence behavior. An external observer also completed the questionnaire. In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire.

\hypertarget{behavioral-data}{%
\subsubsection{Behavioral data}\label{behavioral-data}}

The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab. Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles. One camera was installed to film the class from the side. Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back. Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.

\hypertarget{eyetracking-data}{%
\subsubsection{Eyetracking data}\label{eyetracking-data}}

A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants. The head unit is a measuring device with different sensitive sensors. A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds. Infrared light illuminators support the eye tracking sensors which record the eye orientation. The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second. The scene camera has a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height). The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.

\hypertarget{coding-data-preparation-reliability}{%
\subsection{Coding/ Data preparation/ Reliability}\label{coding-data-preparation-reliability}}

The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes.
The scales on the quality of teaching are a validated questionnaire (Helmke et al. (2014)). Whereas the scales on the teacher's presence behavior were derived from the research literature (Brophy (1986); Kiel, Frey, Weiß, and Weiss (2013); Kounin (2006); Marzano (2007); Nolting (2012)) and were used in the pilot for the first time.

@@

\includegraphics{paper_1_supplement_files/figure-latex/boxplot scales-1.pdf}

\hypertarget{behavioral-data-1}{%
\subsubsection{Behavioral Data}\label{behavioral-data-1}}

The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz and Rädiker (2019)). The following coding scheme was developed:

First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher. The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.

\begin{verbatim}
## 'data.frame':    325 obs. of  7 variables:
##  $ Dokumentgruppe  : chr  "kodiert von Anna" "kodiert von Anna" "kodiert von Anna" "kodiert von Anna" ...
##  $ Dokumentname    : chr  "Aperol_pilot_01_01_expert_D_cam4" "Aperol_pilot_01_01_expert_D_cam4" "Aperol_pilot_01_01_expert_D_cam4" "Aperol_pilot_01_01_expert_D_cam4" ...
##  $ Code            : chr  "Phase\\lesson begin" "speaking time\\teacher" "speaking time\\teacher" "speaking time\\student" ...
##  $ Anfang          : chr  "0:00:44,0" "0:00:44,3" "0:00:49,2" "0:00:51,0" ...
##  $ Ende            : chr  "0:00:44,2" "0:00:47,2" "0:00:50,7" "0:00:52,7" ...
##  $ Fläche          : chr  "00:00:00,2" "00:00:02,8" "00:00:01,4" "00:00:01,6" ...
##  $ Abdeckungsgrad..: num  0.04 0.39 0.19 0.22 0.12 0.13 0.19 1.58 7.3 0.54 ...
\end{verbatim}

\begin{verbatim}
##        Dokumentgruppe Dokumentname  Code Anfang  Ende Fläche Abdeckungsgrad..
##   [1,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##   [2,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##   [3,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##   [4,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##   [5,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##   [6,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##   [7,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##   [8,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##   [9,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [10,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [11,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [12,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [13,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [14,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [15,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [16,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [17,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [18,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [19,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [20,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [21,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [22,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [23,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [24,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [25,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [26,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [27,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [28,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [29,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [30,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [31,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [32,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [33,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [34,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [35,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [36,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [37,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [38,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [39,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [40,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [41,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [42,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [43,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [44,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [45,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [46,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [47,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [48,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [49,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [50,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [51,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [52,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [53,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [54,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [55,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [56,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [57,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [58,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [59,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [60,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [61,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [62,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [63,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [64,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [65,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [66,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [67,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [68,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [69,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [70,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [71,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [72,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [73,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [74,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [75,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [76,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [77,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [78,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [79,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [80,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [81,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [82,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [83,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [84,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [85,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [86,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [87,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [88,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [89,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [90,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [91,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [92,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [93,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [94,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [95,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [96,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [97,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [98,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
##  [99,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [100,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [101,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [102,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [103,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [104,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [105,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [106,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [107,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [108,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [109,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [110,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [111,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [112,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [113,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [114,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [115,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [116,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [117,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [118,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [119,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [120,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [121,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [122,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [123,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [124,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [125,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [126,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [127,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [128,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [129,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [130,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [131,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [132,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [133,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [134,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [135,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [136,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [137,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [138,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [139,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [140,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [141,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [142,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [143,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [144,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [145,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [146,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [147,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [148,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [149,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [150,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [151,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [152,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [153,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [154,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [155,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [156,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [157,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [158,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [159,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [160,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [161,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [162,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [163,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [164,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [165,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [166,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [167,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [168,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [169,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [170,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [171,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [172,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [173,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [174,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [175,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [176,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [177,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [178,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [179,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [180,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [181,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [182,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [183,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [184,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [185,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [186,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [187,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [188,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [189,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [190,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [191,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [192,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [193,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [194,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [195,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [196,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [197,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [198,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [199,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [200,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [201,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [202,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [203,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [204,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [205,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [206,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [207,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [208,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [209,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [210,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [211,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [212,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [213,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [214,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [215,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [216,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [217,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [218,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [219,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [220,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [221,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [222,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [223,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [224,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [225,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [226,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [227,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [228,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [229,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [230,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [231,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [232,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [233,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [234,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [235,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [236,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [237,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [238,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [239,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [240,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [241,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [242,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [243,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [244,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [245,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [246,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [247,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [248,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [249,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [250,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [251,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [252,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [253,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [254,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [255,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [256,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [257,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [258,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [259,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [260,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [261,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [262,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [263,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [264,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [265,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [266,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [267,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [268,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [269,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [270,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [271,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [272,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [273,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [274,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [275,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [276,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [277,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [278,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [279,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [280,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [281,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [282,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [283,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [284,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [285,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [286,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [287,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
## [288,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
